---
title: "Jaafari Collaboration"
author: "Malorie Hughes"
output: 
  flexdashboard::flex_dashboard:
    source_code: embed
   
    vertical_layout: fill
    theme: bootstrap
---



```{css}


.navbar-inverse {
 
  filter: grayscale(30%);
  filter: opacity(80%);
 
  background-repeat: no-repeat;
  padding: 3px
  
}


.navbar-brand {
color:black!important;
font-size:15pt;
font-weight: 310; 

font-family: 'Helvetica Neue', sans-serif;
 margin: 8px 250px 8px 46px;
 
 
}
.navbar-title {
  color: #ffffff; font-family: 'Lato', sans-serif; font-size: 54px; font-weight: 300; line-height: 58px; margin: 10px; padding: 10px; }

p { font-family: 'Helvetica Neue', sans-serif;  color: #777777; margin: 2px 15px 2px 15px; font-weight: 260; }

.navbar-inverse .navbar-text {
  color: #ffffff;
}


.navbar-inverse .navbar-nav > li > a {
  color: #404040
  font-weight: 310; 

font-family: 'Helvetica Neue', sans-serif;
}


blockquote { font-family: 'Bitter',serif; font-size: 24px; border-left: 5px solid #d0d0d0;  margin: 0 0 1 0px; color: #a9a9a9; padding: -15px -15px -15px -15px; text-align: center;
border-right: 5px solid #d0d0d0; text-transform: uppercase;
-moz-box-shadow: 2px 2px 15px #ccc;
  -webkit-box-shadow: 2px 2px 15px #ccc;
  box-shadow: 2px 2px 15px #ccc;
}

ul{
 list-style:square;  display: inline-block;   margin: 10px; color: #777777;
 
}

.level1 { margin-top: 10px; margin-bottom: 12px}

.footer {
    position: fixed;
    left: 0;
    bottom: 0;
    width: 100%;
    
   
    text-align: right;
}

.dygraph-title {
  color: navy;
  font-weight: bold;
}
.dygraph-axis-label {
  font-size: 11px;
}

```	
<div class="footer">
  <p> mhughes@npr.org |  Updated  <script> document.write(new Date().toLocaleDateString()); </script> </p>
</div>


<style type="text/css">
h4.date {
  text-align: right;
}
.sidebar { overflow: auto; }
</style>





 
```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(tidyverse)
library(stargazer)
library(highcharter)
library(DT)
RAW_PATH<-"../DATA/RAW/"
data<-read_csv(paste0(RAW_PATH,"VCAP_STATE_TOTALS_MASTER.csv"))

```


```{r}
export <- list(
  list(text="PNG image",
       onclick=JS("function () { 
                  this.exportChart({ type: 'image/png' }); }")),
  list(text="JPEG image",
       onclick=JS("function () { 
                  this.exportChart({ type: 'image/jpeg' }); }")),
  list(text="SVG vector image",
       onclick=JS("function () { 
                  this.exportChart({ type: 'image/svg+xml' }); }")),
  list(text="PDF document",
       onclick=JS("function () { 
                  this.exportChart({ type: 'application/pdf' }); }")),
  list(separator=TRUE),
  list(text="CSV document",
       onclick=JS("function () { this.downloadCSV(); }")),
  list(text="XLS document",
       onclick=JS("function () { this.downloadXLS(); }"))
  
)


```



```{r}
#head(data,10)
#tail(data,10)
# remove NA counties and division by zero
data<-data %>% filter(!is.na(County)) %>%
  mutate(Avg_Paid=replace(Avg_Paid, Avg_Paid=='#DIV/0!', 0)) %>% 
  as.data.frame() 

# remove characters from $$ columns and convert to numeric
data$Avg_Paid<-gsub('$','',data$Avg_Paid,fixed=TRUE)
data$Avg_Paid<-gsub(',','',data$Avg_Paid)
data$Avg_Paid<-as.numeric(as.character(data$Avg_Paid)) # as.character first to be safe.

data$Total_Paid<-gsub('$','',data$Total_Paid,fixed=TRUE)
data$Total_Paid<-gsub(',','',data$Total_Paid)
data$Total_Paid<-as.numeric(as.character(data$Total_Paid)) # as.character first to be safe.

data.clean<-data%>% filter(!is.na(County)) %>%mutate(County=replace(County,County=="Out of state","Out Of State"))%>%
  mutate(County=replace(County,County=="No county","No County"))%>%
filter(!County %in% c("TOTAL"
                      ,"Does not include claims being processed"
                     , "OTHER"
                   , "No County"
                    ,"Out Of State"
                     ) ) %>% data.frame()
```



```{r,plots}


data.county<-data.clean %>% group_by(State,County) %>% filter(Year>=2013)%>%summarize(county_state=paste0(unique(County),", ",unique(State))
  ,avg_processed=round(mean(Processed,na.rm=TRUE),2)
                                        , avg_num_paid=round(mean(Num_Paid,na.rm=TRUE),2)
                                        , total_processed=sum(Processed,na.rm=TRUE)
                                        ,total_num_paid=sum(Num_Paid,na.rm=TRUE)
                                       ,percent_unpaid=round(100*(sum(Processed,na.rm=TRUE)-sum(Num_Paid,na.rm=TRUE))/sum(Processed,na.rm=TRUE))
                                        ) 

data.county<-data.county %>% data.frame()%>% arrange(desc(percent_unpaid)) %>% mutate(county_state=factor(county_state,levels=county_state))
#%>% filter(between(row_number(), 1, 15))




x <- c( "State","Num. Claims Processed","Num. Claims Paid","Percent Claims Unpaid")

y <- sprintf("{point.%s}", c( "State","total_processed","total_num_paid","percent_unpaid"))
tltip <- tooltip_table(x, y)

plot1<-highchart()%>%
  hc_add_series(data.county[1:25,], "column", hcaes(x = as.character(county_state), 
                                        y =percent_unpaid ,color=State   )) %>%
  hc_yAxis( title = list(text = "100*(Total Unpaid)/(Total Processed)")) %>% 
  hc_xAxis(title = list(text = " "),type="category" )%>% 
  hc_tooltip(useHTML = TRUE, headerFormat = "", pointFormat = tltip)%>%
  hc_plotOptions(column = list(itemStyle=list( fillOpacity = 0.1)))%>% 
  hc_title(text="Percent of Processed Claims that went Unpaid")   %>%
  hc_legend(enabled = FALSE, itemStyle=list(  opacity = 0.75,fontWeight="regular")) %>%
hc_exporting(
    enabled = TRUE, filename="top25counties_percentClaimsUnpaid"
     , formAttributes=list(target="_blank"),
               buttons=list(contextButton=list(
               text="Export", theme=list(fill="transparent"),
                 menuItems=export)) )
  #%>% hc_add_theme(hc_theme_elementary())


#######################################################
############### PLOT 2

top_five_per_state<-data.county%>%filter(percent_unpaid!="-Inf") %>% group_by(State) %>%
  top_n(n = 5, wt = percent_unpaid) %>% arrange(State,desc(percent_unpaid))
#mutate(County=as.character(County))



x <- c( "State","Num. Claims Processed","Num. Claims Paid","Percent Claims Unpaid")

y <- sprintf("{point.%s}", c( "State","total_processed","total_num_paid","percent_unpaid"))
tltip <- tooltip_table(x, y)

plot2<-highchart()%>%
  hc_add_series(top_five_per_state, "bar", hcaes(x = county_state, 
                                        y =percent_unpaid,group=State    )) %>%
  hc_yAxis( title = list(text = "100*(Total Unpaid)/(Total Processed)"),max=100) %>% 
 hc_xAxis(title = list(text = " "),type="category" )%>% 
  hc_tooltip(useHTML = TRUE, headerFormat = "", pointFormat = tltip)%>%
  hc_title(text="Top Five Counties per State: Percent of Unpaid Claims")   %>%
  hc_legend(enabled = FALSE, itemStyle=list(  opacity = 0.75,fontWeight="regular"))%>%
hc_exporting(
    enabled = TRUE, filename="statesTop5counties_percentClaimsUnpaid"
     , formAttributes=list(target="_blank"),
               buttons=list(contextButton=list(
               text="Export", theme=list(fill="transparent"),
                 menuItems=export)) )
# %>% hc_add_theme(hc_theme_elementary())

```

Exploration
=======================================================================

Column  {.tabset}
-------------------------------------


### Processed VS Paid

Which counties experience the largest differences between claims processed and claims paid? 


```{r,echo=FALSE}
plot1
```


### States' Top Five Unpaid
Which counties have the highest percentage of unpaid claims in each state?


```{r,echo=FALSE}
plot2
```

### Percent Denials

```{r}
library(DT)

RAW_PATH<-"~/Documents/2018/02_Jaafari_Proj/DATA/RAW/"
data<-read_csv(paste0(RAW_PATH,"VCAP_STATE_TOTALS_MASTER.csv"))

data<-data %>% filter(!is.na(County)) %>%
  mutate(Avg_Paid=replace(Avg_Paid, Avg_Paid=='#DIV/0!', 0)) %>% 
  as.data.frame() 

# remove characters from $$ columns and convert to numeric
data$Avg_Paid<-gsub('$','',data$Avg_Paid,fixed=TRUE)
data$Avg_Paid<-gsub(',','',data$Avg_Paid)
data$Avg_Paid<-as.numeric(as.character(data$Avg_Paid)) # as.character first to be safe.

data$Total_Paid<-gsub('$','',data$Total_Paid,fixed=TRUE)
data$Total_Paid<-gsub(',','',data$Total_Paid)
data$Total_Paid<-as.numeric(as.character(data$Total_Paid)) # as.character first to be safe.

data.clean<-data%>% filter(!is.na(County)) %>%mutate(County=replace(County,County=="Out of state","Out Of State"))%>%
  mutate(County=replace(County,County=="No county","No County"))%>%
  filter(!County %in% c("TOTAL"
                        ,"Does not include claims being processed"
                        , "OTHER"
                        , "No County"
                        ,"Out Of State"
  ) ) %>% data.frame()




  
  
data.county<-data.clean %>% group_by(State,County) %>%summarize(county_state=paste0(unique(County),", ",unique(State))
                                                                                      ,avg_processed_per_year=round(mean(Processed,na.rm=TRUE),2)
                                                                , total_processed_all_years=sum(Processed,na.rm=TRUE)
                                                                ,percent_denied=round(100*sum(Denied,na.rm=TRUE)/(sum(Processed,na.rm=TRUE)))
                                                                ,total_denied=sum(Denied,na.rm=TRUE)
                                                                                      , avg_num_paid=round(mean(Num_Paid,na.rm=TRUE),2)
                                                                                      
                                                                                      ,total_num_paid=sum(Num_Paid,na.rm=TRUE)
                                                                
                                                                                      ,percent_unpaid=round(100*(sum(Processed,na.rm=TRUE)-sum(Num_Paid,na.rm=TRUE))/sum(Processed,na.rm=TRUE))
) %>% filter(avg_processed_per_year>20)

data.county<-data.county %>% data.frame()%>% arrange(desc(percent_denied)) %>% mutate(county_state=factor(county_state,levels=county_state))
#%>% filter(between(row_number(), 1, 15))


datatable(data.county,  rownames = FALSE, extensions = c('Buttons','FixedColumns'),  options = list(pageLength = 100, fixedColumns = list(leftColumns = 1),
                                                                                                dom = 'Bfrtip',columnDefs = list(list(searchable = FALSE, targets = 1))
                                                                                                , 
                                                                                                buttons = 
                                                                                                  list( list(
                                                                                                    extend = 'collection',
                                                                                                    buttons = list(list(extend='csv',
                                                                                                                        filename = 'county_level_summary'),
                                                                                                                   list(extend='excel',
                                                                                                                        filename = paste0('unrestricted_CrossPromo_') ) ),text="Download"
                                                                                                    
                                                                                                    
                                                                                                  ))))






```



### Top 3 Denials


```{r}
top_three_per_state<-data.county %>% group_by(State) %>% filter(percent_denied>0)%>%
  top_n(n = 3, wt = percent_denied) %>% arrange(State,desc(percent_denied))


datatable(top_three_per_state,  rownames = FALSE, extensions = c('Buttons','FixedColumns'),  options = list(pageLength = 100, fixedColumns = list(leftColumns = 1),
                                                                                                dom = 'Bfrtip',columnDefs = list(list(searchable = FALSE, targets = 1))
                                                                                                , 
                                                                                                buttons = 
                                                                                                  list( list(
                                                                                                    extend = 'collection',
                                                                                                    buttons = list(list(extend='csv',
                                                                                                                        filename = 'top3counties_percentDenied'),
                                                                                                                   list(extend='excel',
                                                                                                                        filename = paste0('top3counties_percentDenied') ) ),text="Download"
                                                                                                    
                                                                                                    
                                                                                                  ))))




```



### New York: Denied HIC

```{r}
ny_denied<-data.clean %>% filter(State=="New York") %>% group_by(County) %>% mutate(Denied=as.integer(as.character(Denied))) %>%mutate(Denied_HIC=as.integer(as.character(Denied_HIC))) %>%
  summarize(Total_Denied=sum(Denied,na.rm=TRUE)
                  ,   Total_Denied_HIC=sum(Denied_HIC,na.rm=TRUE)
                ,Avg_Denied=round(mean(Denied,na.rm=TRUE))
                ,Avg_Denied_HIC=round(mean(Denied_HIC,na.rm=TRUE))
                     ,percent_denied_HIC=round(100*sum(Denied_HIC,na.rm=TRUE)/sum(Denied,na.rm=TRUE))
                                                                                        )
  


datatable(ny_denied,  rownames = FALSE, extensions = c('Buttons','FixedColumns'),  options = list(pageLength = 100, fixedColumns = list(leftColumns = 1),
                                                                                                dom = 'Bfrtip',columnDefs = list(list(searchable = FALSE, targets = 1))
                                                                                                , 
                                                                                                buttons = 
                                                                                                  list( list(
                                                                                                    extend = 'collection',
                                                                                                    buttons = list(list(extend='csv',
                                                                                                                        filename = 'NY_counties_denied_HIC'),
                                                                                                                   list(extend='excel',
                                                                                                                        filename = paste0('NY_counties_denied_HIC') ) ),text="Download"
                                                                                                    
                                                                                                    
                                                                                                  ))))





# filter(Total_Denied>20)%>%
#  top_n(n = 3, wt = percent_denied) %>% arrange(State,desc(percent_denied))




```


### State-Level
```{r}

state_totals<- read_csv("/Users/MHughes/Documents/2018/02_Jaafari_Proj/DATA/RAW/STATE_TOTALS_2010-2015.csv")
#For New York (2011-2015):
#  Out of total murder claims, what percentage were denied b/c of a hand in their own crime?

state_sum<-state_totals%>% group_by(State) %>% summarize(Percent_of_Denials_bc_HIC=round(100*sum(`Denied b/c HIC`,na.rm=TRUE)/sum(`Claims Denied`,na.rm=TRUE),2)
                                              ,Percent_Murder_Claims_Denied_bc_HIC=round(100*sum(`Denied b/c HIC`,na.rm=TRUE)/sum(`Murder Claims`,na.rm=TRUE))
                                              )




datatable(state_sum,  rownames = FALSE, extensions = c('Buttons','FixedColumns'),  options = list(pageLength = 100, fixedColumns = list(leftColumns = 1),
                                                                                                dom = 'Bfrtip',columnDefs = list(list(searchable = FALSE, targets = 1))
                                                                                                , 
                                                                                                buttons = 
                                                                                                  list( list(
                                                                                                    extend = 'collection',
                                                                                                    buttons = list(list(extend='csv',
                                                                                                                        filename = 'state_level_summary'),
                                                                                                                   list(extend='excel',
                                                                                                                        filename = paste0('state_level_summary') ) ),text="Download"
                                                                                                    
                                                                                                    
                                                                                                  ))))

```

### Denials by % Minority

```{r}

percent_minority<-read_csv("/Users/MHughes/Documents/2018/02_Jaafari_Proj/DATA/RAW/CensusRacialData2013.csv")

percent_minority<- percent_minority%>%  mutate(percent_nonwhite=round(100-White,2))

percent_minority$minority_binned<-NA
percent_minority$minority_binned=ifelse(percent_minority$percent_nonwhite<=25,25,percent_minority$minority_binned)
percent_minority$minority_binned=ifelse(percent_minority$percent_nonwhite>25 & percent_minority$percent_nonwhite<=50 ,50,percent_minority$minority_binned)
percent_minority$minority_binned=ifelse(percent_minority$percent_nonwhite>50 & percent_minority$percent_nonwhite<=75 ,75,percent_minority$minority_binned)
percent_minority$minority_binned=ifelse(percent_minority$percent_nonwhite>75 & percent_minority$percent_nonwhite<=100 ,100,percent_minority$minority_binned)


counties_with_race<-merge(data.county,percent_minority,by.x=c("County","State"),by.y=c("County","State"))
counties_with_race<-counties_with_race%>%filter(avg_processed_per_year>20& !State %in% c("New Jersey","Pennsylvania"))
state_denials_summary<-counties_with_race %>%group_by(State,minority_binned)%>%
 summarize(Average_Percent_Denied=round(mean(percent_denied)))
  
  

datatable(state_denials_summary,  rownames = FALSE, extensions = c('Buttons','FixedColumns'),  options = list(pageLength = 100, fixedColumns = list(leftColumns = 1),
                                                                                                            dom = 'Bfrtip',columnDefs = list(list(searchable = FALSE, targets = 1))
                                                                                                            , 
                                                                                                            buttons = 
                                                                                                              list( list(
                                                                                                                extend = 'collection',
                                                                                                                buttons = list(list(extend='csv',
                                                                                                                                    filename = 'avgPercentDenied_by_PercentMinority'),
                                                                                                                               list(extend='excel',
                                                                                                                                    filename = paste0('avgPercentDenied_by_PercentMinority') ) ),text="Download"
                                                                                                                
                                                                                                                
                                                                                                              ))))



```

### High/Low Minority Counties

```{r}


top_three_minority_counties <- counties_with_race%>% group_by(State) %>% top_n(n = 3, wt = percent_nonwhite) %>% arrange(State,percent_nonwhite) %>% select(State,County, minority_binned,Black,Latino,`Native American`,percent_nonwhite, percent_denied)

lowest_three_minority_counties<- counties_with_race%>% group_by(State) %>% top_n(n = -3, wt = percent_nonwhite) %>% arrange(State,percent_nonwhite) %>% select(State,County, minority_binned,Black,Latino,`Native American`, percent_nonwhite, percent_denied)

high_low_minority<-rbind(top_three_minority_counties,lowest_three_minority_counties)
high_low_minority<-high_low_minority%>%arrange(State,percent_nonwhite) 

datatable(high_low_minority,  rownames = FALSE, extensions = c('Buttons','FixedColumns'),  options = list(pageLength = 100, fixedColumns = list(leftColumns = 1),
                                                                                                           dom = 'Bfrtip',columnDefs = list(list(searchable = FALSE, targets = 1))
                                                                                                           , 
                                                                                                           buttons = 
                                                                                                             list( list(
                                                                                                               extend = 'collection',
                                                                                                               buttons = list(list(extend='csv',
                                                                                                                                   filename = 'avgPercentDenied_by_PercentMinority'),
                                                                                                                              list(extend='excel',
                                                                                                                                   filename = paste0('avgPercentDenied_by_PercentMinority') ) ),text="Download"
                                                                                                               
                                                                                                               
                                                                                                             ))))%>%
  
  formatStyle(c("State","County", "minority_binned","Black","Latino","percent_nonwhite", "percent_denied"),fontSize='85%')




```

### County Data Cleaned

```{r}
#counties_with_race2<- counties_with_race %>%filter(avg_processed_per_year>20 )
datatable(counties_with_race,  rownames = FALSE, extensions = c('Buttons','FixedColumns'),  options = list(pageLength = 100, fixedColumns = list(leftColumns = 1),
                                                                                                           dom = 'Bfrtip',columnDefs = list(list(searchable = FALSE, targets = 1))
                                                                                                           , 
                                                                                                           buttons = 
                                                                                                             list( list(
                                                                                                               extend = 'collection',
                                                                                                               buttons = list(list(extend='csv',
                                                                                                                                   filename = 'counties_with_race_data'),
                                                                                                                              list(extend='excel',
                                                                                                                                   filename = paste0('counties_with_race_data') ) ),text="Download"
                                                                                                               
                                                                                                               
                                                                                                             ))))%>%
  
  formatStyle(c("State","County", "minority_binned","Black","Latino","percent_nonwhite", "percent_denied"),fontSize='85%')



```

### Model Summary

####
**Interpretation:** after controlling for the state and total claims processed, *a 10% increase in a county's non-white population corresponded to a 3.9% increase in denials.*
```{r}
mod2<-lm(log(total_denied)~percent_nonwhite +factor(State) +  log(total_processed_all_years),data=counties_with_race)
summary(mod2)#, robust=TRUE)

```
####

```{r}

counties_with_race$predicted_log<-mod2$fitted.values
counties_with_race$est_percent_increased_denials<-100*counties_with_race$percent_nonwhite*(exp(0.003899)-1)

plot(counties_with_race$percent_nonwhite , counties_with_race$percent_denied)
lines(counties_with_race$percent_nonwhite, counties_with_race$est_percent_increased_denials,col="red")

#plot(counties_with_race$percent_nonwhite , counties_with_race$total_denied)
#lines(counties_with_race$percent_nonwhite, counties_with_race$est_percent_increased_denials,col="red")


#abline(lm(log(counties_with_race$total_denied)~counties_with_race$percent_nonwhite), col="red")
```



